---
title: "2/24/15"
author: "(>^-^)>"
date: "Tuesday, February 24, 2015"
output: html_document
---
#Histograms#
```{r}
library(MASS)
?quine

hist(quine$Days)
with(data=quine, hist(Days))

library(ggplot2)
ggplot(data=quine, aes(x=Days))+
  geom_histogram(fill="green",color="black")+
  theme_bw()+
  facet_grid(Age~.)

ggplot(data=quine, aes(x=Days))+
  geom_histogram(fill="violetred",color="black")+
  theme_bw()+
  facet_grid(Age~Sex)

ggplot(data=quine, aes(x=Days))+
  geom_density(fill="seagreen2",color="black")+
  theme_bw()+
  facet_grid(Age~Sex)

#Three S's 
#Shape - unimodal, skewed to the right
#Center - median for skewed, mean for symetric
#Spread - If appropriate for center is median then for spread it would be IQR (Interquartile range).  SYmetric you would us standard deviation.
```


#Scatter Plots#
```{r}
library(car)
library(MASS)
str(Boston)
?Boston
plot(Boston)

plot(Boston$medv~Boston$lstat)
par(mfrow=c(1,2))  #1 row two columns
plot(medv~lstat,data=Boston,col="purple", pch=19, cex=.25)
plot(medv~rm,data=Boston, col="blue", pch=19, cex=.25)
par(mfrow=c(1,1)) #back to normal, 1 row one column

cor(Boston) #correlation coeficcients 
cor(Boston$medv, Boston$lstat)
cor(Boston$medv, Boston$rm)

#mod1<-lm(y~x, data = DF) ,general formula
mod1<-lm(medv~lstat, data=Boston)
mod1
summary(mod1)
pt(-1.12,504)
